Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-20 PaperBCJ.tex

\section{Introduction}
During the last centuries, significant progress has taken place in science and technology developments. Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial sectors, providing new means to approach problems differently. 
\\

@@

Nowadays, one of agriculture challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation. There are studies that show the impact of Weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha. Currently, growing development of Artificial Vision and Machine Learning algorithms allow researchers to propose solutions for Weed Segmentation in Crops. 
\\

@@

The development of the model for the weed and maize identification algorithm using convolutional neural networks is described below.
\\
\subsection{Hardware}

Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes. Debido a la popularidad de la computacion por GPU, fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de procesamiento y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M. Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar los tiemposde clasificacion de imagenes en las arquitecturas de red.  \\

For the training and image capturing stages, the following elements were used: a Raspberry Pi 3 with Pi Camera V2.1 for image acquisition, it was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M. Also it was neccesary to consider the use of a CPU Core i7 2.7 Ghz, 8 cores and the CPU of the Raspberry Pi 3, a ARM Cortex-A53, 1.2GHz, 4 cores for testing the classification of images of the Network.   
\\

@@

For the application in this documents it requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{opencv_library} in this  case, it was used for acquisition and segmentation of the sample images. Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{jia2014caffe} with fully support of CUDA GPU Computation Library and a generous database of resources for learning,	
\\

@@

Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province, on the center of the Ecuadorian Highlands region P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose. \\

@@

Samples were obtained from images captured in those maize fields , we considered to choose maize crops where we could visually discriminate the plants of the crop and the weed. Maize in stages V3-V7(3-7 leafs) \cite{fassio1998maiz} were used to take samples. To record the samples we centered the camera over the target plant, insuring that the capture shows all features of the maize plant, it was possible by monitoring the get of samples by an external display. An examples of the images captured are shown below.

@@

Also it was neccesary to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the Network to discriminate both classes of the Dataset. \\

@@

Then, through a digital image processing, as first stage the image was normalized in its green channel, it improves the detection of green color due it eliminates lights and shadows of the image, after we extracted the green color to obtain a grayscale image, through the next equation described by Wang, Meng, Luo and Mei \cite{wang2013path}, then we applied a OTSU Thresholding to grayscale image in order to obtain a binary mask.  
\begin{equation}
	S = 2*G - R - B
\end{equation}

@@

After the images were segmented to differentiate them from the soil and other non-plant elements, the original images were masked with the binary mask to provide the dataset features of color of the Maize and Weed. Once the segmented images were obtained, we were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document, later, the images were saved in a png format. The process described before, was illustrated in the next figure. \\

@@

It should be noted that we had manually labeled the samples in two classes, maize and weed, having no account that the images are not repeated. In the following image we present the final results of the processed images that conform the dataset.\\

@@

Once we completed the processing of the images, it were obtained 2835 images of Maize and 880 images of Weed, Lee \textit{et. al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{sladojevic2016deep}  they mention that this allows to reduce the overfitting and to improve the precision in the training, reason why we made 11 rotations each 30 degrees, obtaining in this way to increase the dataset in 12 times and have better chances of recognizing plants that are in any orientation. \\

@@

For the Validation Phase, we had chosen randomly a fifth part of the total images of each class, so we have the following chart with the distribution of the dataset.

@@

	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{sharif2014cnn}. Their are also applied in Precision Agriculture \cite{potena2016fast} for the correct identification of plants.\\

@@

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
  Accuracy(\%) & 86.48 & 93.86 & 95.33 & 80.4 \\
  Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\end{table}

@@

Inside of the shown parameters in the Table \ref{table:2}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission near to human classification.\\

@@

Although results given for the net are excellents, one of the main purposes of this paper is the implementation in real time, so the number of parameters to be computed must be a problem, so we considered to modify the net in order to improve the processing time. To achive this, it was neccesary to reduce the number of filters of cNET from 64 to 16.\\

@@

This reduction permitted to reduce the number of parameters to 1651376(it's a 25\% of parameters than the original net), and what about the precision of the net, it was slighty affected but it reach a 97.2\% of accuracy.\\

@@

So, the complete network model is formed as follows: the input layer where an RGB image 64x64 pixels, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel, this layer  obtaining only the main characteristics of the image, then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2, then again a second layer of convolution is applied that has 16 filters, size of kernel 5 and a stride of 1, followed by a new layer of pooling with a kernel size and stride of 2, so the result image was has size of 16x16x16 and finally the net is completed with three fully-connected layers, the first with 384 neurons, the next with 192 and the last with 2 neurons which represent the both classes  the layers of type fully-connected with a total of 478 neurons, where the last two neurons that is the output represent the two classes to classify, the result model is shown in the next graph.\\

@@

In the graph of training shown below, we can appreciate the final result of the net accuracy, 9000 iterations were neccesary to reduce the Loss value to its minimun and the architecture shows that it can reach an acceptable accuracy with few iterations. Note that by reducing the number of filters the network gained accuracy because the dataset does not have so much features learn, so the net found a better solution with a less number of parameters.      \\

>>>>

\section{Introduction}
During the last centuries, significant progress has taken place in science and technology developments. Significant milestones in diverse areas such as communications, numerical computer control and the miniaturization of components have benefited industrial sectors, providing new means to approach problems in a different manner. 
\\

@@

Nowadays, one of agriculture's challenges is the development of precision agriculture techniques focused on Weed and Crop segmentation. There are studies that show the impact of Weed in corn crops \cite{suarez2005distintos}; its yield is affected by 5000 kg/ha. Currently, growing development of Artificial Vision and Machine Learning algorithms allow researchers to propose solutions for Weed Segmentation in Crops. 
\\

@@

The model development for weed and maize identification algorithm using convolutional neural networks is described below.
\\
\subsection{Hardware}

Para la etapa de entranamiento y captura de imagenes, los siguientes elementos fueron utilizados: Una Raspberry Pi 3 con su modulo de camara V2.1 para la adquisicion de imagenes, fue configurado para obtener video en resolucion de 1280x720 pixeles con el fin de obtener mayor detalle en la segmentacion de imagenes. Debido a la popularidad de la computacion por GPU(COMPLETAR IDEA), fue necesario consider hardware compatible con computacion paralela como las tarjetas graficas fabricadas por NVIDIA, estas tienen la ventaja de poseer mejores tiempos de procesamiento comparados con la CPU, con lo cual se logra optimizar los tiempos de procesamiento y entrenamiento de Modelos de Deep Learning, entonces, utilizamos un computador con una tarjeta Grafica NVIDIA GTX950M. Tambien fue necesario considerar el uso de un CPU Core i7 2.7Ghz, 8 Nucles and el CPU de la propia Raspberry Pi 3, un ARM 3, a ARM Cortex-A53, 1.2GHz, 4 nucles para probar los tiemposde clasificacion de imagenes en las arquitecturas de red.  \\

For the training and image-capturing stages, the following elements were used: a Raspberry Pi 3 with a V2.1 Pi camera for image acquisition. The system was configured to obtain a video at a resolution of 1280x720 pixels in order to get more detail in the segmented images. Due to the popularity of GPU computing(COMPLETAR IDEA), it was necessary to consider hardware compatible with parallel computing such as the Graphic Cards manufactured by NVIDIA. These cards have the advantage of a superior processing speed compared to a CPU in order to optimize image-processing time and deep learning Model's training process, thus the selected device was a computer with a Nvidia graphics card GTX950M. Also, it was necessary to consider the use of a Core i7 2.7 Ghz CPU of 8 cores and the CPU of the Raspberry Pi 3, an ARM Cortex-A53, 1.2GHz, 4 cores (CLARIFICAR IDEA) for testing  classification speed of network images.   
\\

@@

The use of powerful libraries of Image Processing and Deep Learning Development was required due to....  . The use of open software was required in order to provide the system with a certain level of flexibility to extend its use for future prototypes. Thus,  OpenCV library was chosen due to its computational efficiency and focus on real-time applications \cite{opencv_library}; it was used specificaly for sample images acquisition and segmentation. Also, Caffe was considered because it is intended to aid in the training and developing of general-purpose convolutional neural networks and other Deep Lerning models \cite{jia2014caffe} with full support of CUDA GPU computation library and a generous database of resources for MACHINE(?) learning.	
\\

@@

Due to the lack of weed and maize plant datasets, it was necessary to search maize crops in its initial development stage for...(COMPLETAR IDEA). Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples. P\'illaro it is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as: maize, potatoes and a wide variety of fruits. Due to its year-long production season, many maize crops at its initial development stage were found in this area. \\

@@

Samples were obtained from images captured in different maize fields. Crops were weed and maize plants could be visually discriminated were chosen in order to (SUSTENTAR IDEA). Maize at a V3 to V7 develompent stage (3-7 leafs) \cite{fassio1998maiz} were used to take samples. To record the samples, a camera was centered over the target plant, insuring that the capture shows all features of the maize plant. This was achieved by monitoring the obtained samples through an external display. Examples of the images captured are shown below.

@@

Also, it was necessary to obtain images of the most common weed plants of the maize crops in Pillaro, to allow the network to discriminate between the two defined classes of the dataset. \\

@@

Then, through a first-stage digital image processing procedure, the images were normalized in its green channel. This was done in order to improve green color detection based on the elimination of light and shadow in the images. Later, the green color was extracted from the images to obtain a grayscale equivalent; this was done through the following equation described by Wang, Meng, Luo and Mei \cite{wang2013path}. Following, an OTSU Thresholding was applied to the grayscale images in order to obtain a binary mask.  
\begin{equation}
	S = 2*G - R - B
\end{equation}

@@

Afterwards, the images were segmented in order to differentiate them from the soil and other non-plant elements. Original images were masked with the binary mask to provide the dataset with color features of maize and weed plants. Once the segmented images were obtained, images that had a resolution lower than 64x64 pixels were removed because its size was smaller than the size of the network input layer. Besides, the processing of these small images was not convenient since its total area was much smaller than the maize sample images. Following, the images were saved in a png format. The entire process described before is illustrated in the next figure. \\

@@

It should be noted that samples were manually labeled into two classes; maize and weed, making sure that the images are not repeated. In the following image, final results of the processed images that conform the dataset are shown.\\

@@

Once image processing was completed, a set of 2835 maize images and 880 weed images was obtained. Lee \textit{et. al} \cite{lee2015deep} said that once CNN has reached an acceptable accuracy, the dataset can be extended by means of geometric transformations. In addition, \cite{sladojevic2016deep} mention that geometric transformations(?) allow overfitting reduction  and improves the precision in the training process. For this reason, image rotations each 30 degrees were made, obtaining an increment of the dataset by 12 times, thus increasing the chances of recognizing plants that are in any orientation effectively. \\

@@

For the Validation Phase, a fifth part of the total image set of each class was chosen, resulting in the following chart with the distribution of the dataset.

@@

	After the dataset was completed, it was neccesary to classify maize and weed images. Convolutional Neural Networks (CNN) can be used as a highly-accurate method for image classification, these models are complex but efficient with a high rate of discrimination and have proven to provide good results in image classification, object detection, and fine-grained  classification \cite{sharif2014cnn}. CNN are widely used in precision agriculture \cite{potena2016fast} for the correct identification of plants.\\

@@

One of the characteristics of the CNN is that these can have multiple architectures, each architecture can reach different results depending on the application. For the present document we have considered four CNN architectures: two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
  Accuracy(\%) & 86.48 & 93.86 & 95.33 & 80.4 \\
  Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Comparison of the 4 types of CNN}
\label{table:2}
\end{table}

@@

Within parameters shown on table \ref{table:2}, the network that achieved the highest rate of accuracy and lowest rate of loss was considered; clearly the cNET presented a superior performance due to its near-to-human classification precision.\\

@@

Although results given by this type of network are excellent, one of the main purposes of this paper is the implementation of this system in real time. The number of parameters to be computed by the selected network were numerous, so network modifications in order to improve processing time had to be made. To achieve this, it was necessary to reduce the number of filters of cNET from 64 to 16.\\

@@

This filter reduction permitted to decrease the number of parameters to 1651376 (this represents only 25\% of the original network parameters) without compromising the network precision in a significant way; it still reached a 97.2\% of accuracy.\\

@@

So, the complete network model was conformed by the following components: an input layer where an RGB image of 64x64 pixels is received, followed by a convolution layer of 16 filters, a kernel of 5 and a stride of 1 pixel (this layer only obtains the main characteristics of the image), then a pooling layer is applied, which has the function to find the maximum values of the previous layer with a kernel size and stride of 2 (QUE?), then again a second layer of convolution that has 16 filters is applied, size of kernel 5 and a stride of 1 (QUE), followed by a new layer of pooling with a kernel size and stride of 2, so the resulting image was has size of 16x16x16. Finally the network is completed with three consecutive fully-connected layers; the first with 384 neurons, the next with 192 and the last with 2 neurons. The type of layers fully-connected contain a total of 478 neurons, where the last two neurons that are the output represent the two classes to identify, the result model is shown in the next graph.\\

@@

In training graph shown below we can appreciate the final result of the net accuracy; 9000 iterations were neccesary to reduce the loss value to its minimum and the architecture shows that it can reach an acceptable accuracy with few iterations. Note that by reducing the number of filters the network gained accuracy because the dataset does not have too many features to process, so the network obtained a better solution with a fewer number of parameters.      \\
